Draft Research pt3

### 2019-03-15 draftResearch_pt2.Rmd
Starting join
Some data refresh and join fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r}
pitchers_raw <- "data/depthChartProjections_pitchers_20190308.csv" %>%
  read_csv()
batters_raw <- "data/depthChartProjections_batters_20190308.csv" %>%
  read_csv()

@@

I don't have any objective measure to compare the value between similarly ranked batters and pitchers. I compared a few pairs of players against other expert's rankings and these largely seem to be in line. I'm at a disadvantage without being able to project Quality Starts. However, since I'm walking in with the likely goal of spending early draft capital on hitting and planning to play the waiver wire for two-start/matchup starters, these results should be sufficient. 
### To Do
1. Develop tiers of players (linear model? nearest neighbor?)
2. Replacement level stuff (new section)
3. Take averages of multiple projection sources? 
4. Build team stats based on selections, available players per round?

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet=TRUE)
library(tidyverse)
```

@@

```{r}
pitchers_raw <- "data/depthChartProjections_pitchers_20190308.csv" %>%
  read_csv() %>%
  unique()
batters_raw <- "data/depthChartProjections_batters_20190308.csv" %>%
  read_csv() %>%
  unique()

@@

I don't have any objective measure to compare the value between similarly ranked batters and pitchers. I compared a few pairs of players against other expert's rankings and these largely seem to be in line. I'm at a disadvantage without being able to project Quality Starts. However, since I'm walking in with the likely goal of spending early draft capital on hitting and planning to play the waiver wire for two-start/matchup starters, these results should be sufficient.

### 2019-03-15 draftResearch_pt3.Rmd
Some data refresh and join fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

@@

```{r}
yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
  select(name.full, display_position, positions)

@@

@@

```

```{r}
df_raw %>%
  filter(is.na(display_position)) %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head(25)

df_raw %>%
  filter(Name == "Jose Ramirez") %>%
  select(Name, positions, ADP, ovrl_rank, z_sum) %>%
  head()

fangraphs %>%
  count()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet=TRUE)
library(tidyverse)
library(fuzzyjoin)
```

@@

```{r}
yahoo <- readRDS('data/players_position_eligibility.Rds') %>%
  select(name.full, display_position, positions) %>%
  mutate(name.full = chartr("áéóíñú", "aeoinu", name.full))

yahoo$name.full[yahoo$name.full == 'Daniel Vogelbach'] <- "Dan Vogelbach"
yahoo$name.full[yahoo$name.full == 'Shohei Ohtani (Batter)'] <- "Shohei Ohtani"

@@

fangraphs$Name[fangraphs$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
fangraphs$Name[fangraphs$Name == 'Cedric Mullins II'] <- "Cedric Mullins"
fangraphs$Name[fangraphs$Name == 'Michael Soroka'] <- "Mike Soroka"
fangraphs$Name[fangraphs$Name == 'Nathaniel Lowe'] <- "Nate Lowe"
fangraphs$Name[fangraphs$Name == 'Nathan Karns'] <- "Nate Karns"

@@

df_fuzzy <- fangraphs %>%
  stringdist_full_join(yahoo, by = c("Name" = "name.full"))

df_raw %>% 
  count(is.na(display_position) & is.na(positions))
df_fuzzy %>% 
  count(is.na(display_position) & is.na(positions))
```

#### Orphaned Records after join fixes
1. Replaced accented characters to characters without accents
2. Fuzzy join
3. Yahoo API query for *2500* players (rather than 850)
4. Duplicate Shohei Ohtani records, lack of pitching projections
5. Multiple player minor name mismatches

```{r}
df_fuzzy %>% 
  filter(is.na(display_position) & is.na(positions)) %>%
  View()

yahoo %>% filter("Riley" %>% grepl(name.full))
fangraphs %>% filter("Riley" %>% grepl(Name)) %>% select(Name)
```
